%######################################################
% This file generates the whole report for the project
% Run with "pdflatex report.tex" twice to create pdf
%
% Use *_standalone.tex to generate standalone parts
%######################################################
\documentclass[a4paper, 11pt]{report}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx} % support graphics
\usepackage{hyperref} % links in the document
\usepackage{float} % position of figures
\usepackage{paralist} % inline lists
\usepackage{verbatim} % mulitline comments
\usepackage[table]{xcolor} % table row coloring
\usepackage{booktabs} % Professional tables
\usepackage{tabularx} % Simple column stretching
\usepackage{multirow} % Row spanning
\usepackage{wrapfig} % Wrap text around figures
\usepackage{array}
\usepackage{longtable}

%\setcounter{tocdepth}{1} % Depth of table of contents

% Configure links in pdfs
\hypersetup{
    bookmarksopen=false, % Hide bookmarks menu
    colorlinks=true, % Don't wrap links in colored boxes
}


%############
% Top matter
%############

\title{Wireshark:\\ Automated generation of protocol dissectors}
\author{by\\ Erik Bergersen, Sondre Johan Mannsverk,\\ Terje Snarby,
		Even Wiik Thomassen, Lars Solvoll Tønder,\\ Sigurd Wien
		and Jaroslav Fibichr}
\date{\today}

\begin{document}

%============
% Title page
%============
\maketitle

%==========
% Abstract
%==========
\begin{abstract}
Wireshark is a program used to analyze packet data sent between network nodes.
The purpose of this project was to allow the use of Wireshark to also
decode inter-process communication, which is important, but was difficult to accomplish before.
The project resulted in a stand-alone utility, written in Python, which act as a supporting tool for Wireshark. 
The utility automates the process of generating dissectors for Wireshark from C header files. 
This functionality makes debugging and testing some programs a lot easier.


\end{abstract}

%=========
% Preface
%=========
\pagenumbering{roman}
\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
This report was written for a project in the course TDT4290 
Customer Driven Project at NTNU, on behalf of Thales Norway AS. The project
was executed on behalf of Thales Norway AS between the 30th of August and
the 24th of November.

The project team consisted of seven students from the Norwegian University 
of Technology and Science. Our task was to develop a tool for Wireshark
that could automatically dissect C structs. The utility creates Lua scripts 
which act as package dissectors in Wireshark. 

The team would like to thank our main supervisor Daniela Soares Cruzes
and her assistant Maria Carolina Passos for their continuous input and
guidance throughout the project.

We would also like to thank our customer contacts from Thales, Christian
Tellefsen and Stig Bjørlykke, for invaluable help and feedback during the
development process and also for making the initial requirement 
specification clear and understandable.


%===================
% Table of Contents
%===================
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{Contents}
\tableofcontents

%=================
% List of Figures
%=================
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures

%================
% List of Tables
%================
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables


%###########################
% Planning and Requirements
%###########################
\clearpage
\pagenumbering{arabic}
\part{Planning \& Requirements}

\include{./planning/project_directive}
\include{./planning/plan}
\include{./planning/prestudy}
\include{./planning/requirements}
\include{./planning/product_backlog}
\include{./planning/test_plan}
\include{./planning/architectural}


%#########
% Sprints
%#########
\part{Sprints}
\include{./sprints/sprint1}
\include{./sprints/sprint2}
\include{./sprints/sprint3}
\include{./sprints/sprint4}

\include{./sprints/tests} % Where should this be?


%###########################
% Conclusion and Evaluation
%###########################
\part{Conclusion \& Evaluation}
\include{./evaluation/conclusion}
\include{./evaluation/evaluation}


%############
% Appendices
%############
\part{Appendices}
\appendix
\include{./appendices/acronym}
\include{./appendices/glossary}
\include{./appendices/manual}
\include{./appendices/feedback}


\end{document}

