%=================
\chapter{Sprint 2}
%=================


%------------------------
\section{Sprint Planning}
%------------------------
The first sprint resulted in a solid core for the utility. During the next sprint iteration, the core will be extended with more advanced functionality. After this sprint, the utility will have most of the functionalities it need to work in a real environment, and will probably be able to aid Thales in some of their operations.

Not yet understanding the complexity of all the requirements in the sprint backlog, the team ended in an uncertain person-hours estimate for some work objects. Time will show if we understood the complexity and assigned enough hours to implement it. The more complex, but not so critical functionalities will be part of sprint 3 and 4.   



\subsection{Duration}
%-----------------------
According to the work breakdown structure, \autoref{tab:wbs}, the planning meeting of the second sprint should have been conducted the 5th of October. After a request from the customer to see our planning for the second sprint at the weekly customer meeting, which was scheduled to be before our planning meeting the same day, we decided to advance the planning to the 4th of October. This is to maintain the good relationship to the customer and submit to their preference.

The sprint started with the planning meeting the 4th of October and our work started the following day. The sprint duration is 14 days, and will end the 18th of October with a review meeting.  

\subsection{Sprint Goal}
%-----------------------
The goal of the second sprint is to try and add some more advanced
functionality from sprint one, which aren't the most complex ones.

\subsection{Back Log}
%--------------------
\begin{table}[ht] \small \center
\caption{Sprint 2 Backlog}
\begin{tabularx}{\textwidth}{l l X c c}
	\toprule
	& & & \multicolumn{2}{c}{Hours} \\
	\cmidrule(r){4-5}
	\# & Req. & Description & Est. & Act. \\
	\midrule
	1 & FR1-B & Support members of type enums & - & - \\
	\addlinespace
	2 & FR1-C & Support members of type structs & - & - \\
	\addlinespace
	3 & FR2-B & Support display of structs within structs & - & - \\
	\addlinespace
	4 & FR4-B & Support enumerated named values or a bit strings & - & - \\
	\addlinespace
	5 & FR1-E & Array member & - & - \\
	\addlinespace
	6 & FR5 & Config header/trailer int members & - & - \\
	\addlinespace
	73 & FR4-B & Support enumerated named values or a bit strings & - & - \\
	\midrule
	& & Total: & - & - \\
	\bottomrule
\end{tabularx}
\end{table}

\begin{table}[ht] \small \center
\caption{Sprint 2 Timetable}
\begin{tabularx}{\textwidth}{X c c}
	\toprule
	 & \multicolumn{2}{c}{Hours} \\
	\cmidrule(r){2-3}
	 Description & Est. & Act. \\
	\midrule
	Planning & - & -\\
	\addlinespace
	Implementation & - & -\\
	\addlinespace
	Design & - & -\\
	\addlinespace
	Testing & - & \\
	\midrule
	Total: & - & - \\
	\bottomrule
\end{tabularx}
\end{table}


%----------------------
\section{System Design}
%----------------------


%-----------------------
\section{Implementation}
%-----------------------


%-----------------------
\section{Sprint Testing}
%-----------------------


%--------------------------
\section{Customer Feedback}
%--------------------------


%--------------------------
\section{Sprint Evaluation}
%--------------------------


